---
title: "Getting started with R"
author: Sowmya Janmahanthi
date: 23-09-2024
format: html
---

### Exercise 1 {#sec-1}

* Create a vector of the letters A, B and C.

```{r}
vector <- c("A","B","C")
vector
```
> Your answer as text
> vector
[1] "A" "B" "C"



* Assign the vector to a variable `my_letters`
```{r}
my_letters <- vector
my_letters
```
> my_letters
[1] "A" "B" "C"

* Check the what happens when you run `letters` (just this) on the command line.
```{r}
letters
```

>  [1] "a" "b" "c" "d" "e" "f" "g"
 [8] "h" "i" "j" "k" "l" "m" "n"
[15] "o" "p" "q" "r" "s" "t" "u"
[22] "v" "w" "x" "y" "z"



* What happens when you concatenate two vectors? Add `c(my_letters , my_letters)`
```{r}
c(my_letters , my_letters)
```

> Your answer as text
> c(my_letters , my_letters)
[1] "A" "B" "C" "A" "B" "C"


* Add the number 1 to letters. What happens to the type of the vector?
```{r}
updated_letters<-c(my_letters,"1")
updated_letters
```

> Your answer as text
> updated_letters
[1] "A" "B" "C" "1"


### Exercise 2


1. Create a vector `my_vec` with the numbers from 1 through 8.
2. Apply the operation `+2` to the vector/
3. Add the vector containing 1, 2, 3, 4 to `my_vec`. What do you observe?

```{r}
my_vec <- c(1:8)
my_vec
my_vec+2
sum <- my_vec + c(1,2,3,4)
sum
```
> my_vec
[1] 1 2 3 4 5 6 7 8
> my_vec+2
[1]  3  4  5  6  7  8  9 10
> sum <- my_vec + c(1,2,3,4)
> sum
[1]  2  4  6  8  6  8 10 12

Its adding the vector till the index and again adding to left over elements in vector.


### Exercise 3

* Consider the R output of the matrix below:

```
 [,1] [,2]
 [1,]    4    1
 [2,]    9    5
 [3,]   10    7
```

1. What was one of the correct commands used to write this matrix?
2. Assign the matrix as `A`
3. Check the dimensions
4. Extract the element `5`
5. Add the vector `c(0,0,0)` as a new column and update `A`
6. Modify the element 4 to `0`
7. Compute the transpose of `A`

```{r}
matrix <- matrix(c(4,9,10,1,5,7), nrow = 3, ncol=2)
matrix
```


8. Are any values in `A` larger than 10? 
```{r}
# Your answer in code

```

9. Are all values in `A` smaller than 10?
```{r}
# Your answer in code

```

### Exercise 4

1. Create a function that sums up two values even if provided as characters values

```{r}
# Your answer in code





```


### Exercise 5

1. Create a function that returns the mean, median and standard deviation.

```{r}
# Your answer in code



```


### Exercise 6
1. Create a pipe statement that counts the number of NAs in vector containing numbers, characters and missing values.
The output of `c('1' , "a", NA, "2", NA)` should be 2.

```{r}
# Your answer in code



```


